Spatial Reasoning and Statistical Graphics

### 2014-10-22 Paper/Draft1/TestingVisualAptitude.Rnw
More accurate numbers for ISU students

\section{Results}
Results are based on an evaluation of \Sexpr{nrow(ans)} undergraduate students at Iowa State University. About one-half of the participants were in STEM fields, the others were distributed relatively evenly between agriculture, business, education, and liberal arts. Students were evenly distributed by gender, and were between 18 and 24 years of age with only one exception. This is reasonably representative of the university as a whole; ISU graduates are about 20\% engineering, 16\% business, and 11\% agriculture students, however, these numbers are for completed degrees, not current majors. 
\comment{Heike, can you get better enrollment numbers for current students? My guess is there are more people enrolled in engineering than actually graduate :). }

\newtext{The testing was conducted by two research assistants; the first tested 18 participants, the second tested 20 participants. A comparison of results from each researcher is available in appendix \ref{app:ratests}. }
% \comment{Teensy overview of the demographics - this might end up in an appendix, but then we need to refer to from here. I'd like to know breakdown of men/women, classification, maybe an overview of different majors (not necessarily a breakdown, that might be leading to problems with identifiability)}

>>>>

\section{Results}
Results are based on an evaluation of \Sexpr{nrow(ans)} undergraduate students at Iowa State University. About one-half of the participants were in STEM fields, the others were distributed relatively evenly between agriculture, business, and the social sciences. Students were evenly distributed by gender, and were between 18 and 24 years of age with only one exception. This is reasonably representative of the university as a whole; in the fall 2012 semester, 23\% of students were associated with the college of engineering, 23\% were associated with the college of liberal arts and sciences, 23\% were associated with the college of human sciences, 12\% with the business school, and 14\% with the school of agriculture. \footnote{\url{http://www.ir.iastate.edu/PDFfiles/2012-2013\%20Student\%20Profile.pdf}} 
\newtext{The testing was conducted by two research assistants; the first tested 18 participants, the second tested 20 participants. A comparison of results from each researcher is available in appendix \ref{app:ratests}. }
% \comment{Teensy overview of the demographics - this might end up in an appendix, but then we need to refer to from here. I'd like to know breakdown of men/women, classification, maybe an overview of different majors (not necessarily a breakdown, that might be leading to problems with identifiability)}
